\documentclass[12pt]{article}

%Russian-specific packages
%--------------------------------------
\usepackage[T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english, russian]{babel}
%for search in russian
\usepackage{cmap}
% for markdown style quotes
\usepackage{csquotes}
%--------------------------------------

%Math-specific packages
%--------------------------------------
\usepackage{amsmath}
\usepackage{amssymb}

\def\d{ \mathrm{d} }
\def\norm{ \mathrm{n} }

\usepackage{amsthm}
\newtheorem{lemma}{Лемма}
\newtheorem{definition}{Определение}
\newtheorem*{remark}{Замечание}

%Format-specific packages
%--------------------------------------
\usepackage[left=2cm,
            right=2cm,
            top=1cm,
            bottom=2cm,
            bindingoffset=0cm]{geometry}

%Coding-specific packages
%--------------------------------------
\usepackage{algpseudocode}

%Graphics packages
%--------------------------------------
\usepackage{graphicx}
\usepackage{wrapfig}

\graphicspath{ { ./tex/ } }

\includeonly{
  tex/title
  , tex/introduction
  , tex/radiometry
  , tex/surfaces
  , tex/photometric_stereo
}

\usepackage{tikz}
\usetikzlibrary{
  shapes.geometric
  , intersections
  , calc
  % for angles
  , angles
  , quotes
  , babel
  % ------
 , external
 , arrows.meta
 , patterns
}
\tikzexternalize[prefix=tex/]

\tikzset{
  lighter/.pic={
    code={
      \node[
        draw=black
        , fill=yellow
        , rectangle
        , minimum width=1cm
        , minimum height=0.3cm
      ] (-body) at (0,0) {};

      \filldraw [fill=yellow]
      (-body.north east)
      -- ([shift={(0.3,0.2)}]-body.north east) coordinate (headUpper)
      -- ([shift={(0.3,-0.2)}]-body.south east) coordinate (headLower)
      -- (-body.south east);
      \path ($ (headUpper)!.5!(headLower) $) coordinate (-head);
  }},
  camera/.pic={
    code={
      \node[
        draw=black
        , fill=gray
        , rectangle
        , minimum width=1cm
        , minimum height=0.2cm
      ] (-body) at (0,0) {};

      \filldraw [fill=gray]
      let \n1={0.15} in
      ($ (-body.north east)!.5!(-body.north) $)
      -- ([shift={(0,\n1)}]-body.north east) coordinate (headUpper)
      -- ([shift={(0,\n1)}]-body.north west) coordinate (headLower)
      -- ($ (-body.north)!.5!(-body.north west) $);
      \path ($ (headUpper)!.5!(headLower) $) coordinate (-head);
    }
  }
}

\begin{document}

\include{tex/title}

\newpage
\tableofcontents

\newpage

\include{tex/introduction}

\newpage

\include{tex/radiometry}

\newpage

\include{tex/surfaces}

\newpage

\include{tex/photometric_stereo}

\newpage

\section{Литература}
\begin{enumerate}
  \item Гуревич М. М. Фотометрия. Теория, методы и приборы. — 2-е изд. — Л.: Энергоатомиздат. Ленинградское отделение, 1983. — С. 23—24. — 272 с.
  \item Ying Wu. "Radiometry, BRDF and Photometric Stereo". Northwestern University. Retrieved 2015-03-25.
  \item A. V. Arecchi, T. Messadi, and R. J. Koshel, Field Guide to Illumination, SPIE Press, Bellingham, WA (2007)
  \item Woodham, R.J. 1980. Photometric method for determining surface orientation from multiple images. Optical Engineerings 19, I, 139-144.
  \item R. T. Frankot and R. Chellappa, “A method for enforcing integrability in shape from shading algorithms,” IEEE Transactions on Pattern Analysis and Machine Intelligence, vol. 10, no. 4, pp. 439–451, July 1988
\end{enumerate}
\end{document}
